---
title: "Assignment 2"
output: 
  github_document:
    pandoc_args: --webtex
---

## Question 1

> The weights listed below were recorded in the !Kung census, but heights
> were not recorded for these individuals. Provide predicted heights and 89%
> compatibility intervals for each of these individuals. That is, fill in the table
> below, using model-based predictions.

So, we look at the data from the !Kung census, by loading the proper data:

```{r setup}
library(rethinking)
library(tidyverse)
data(Howell1)
data <- as_tibble(Howell1)
```

Then we create the prior, filtering heights for ages 18 and over only.

```{r}
# filter out younger than 18

data <- data %>% 
  filter(age >= 18)
```
We consider the simple linear regression model used to predict the effect of height on weight:

height = mu + beta1 *(weight - avg_weight)
```{r}
# Simulate data
prior <- tibble(
  mu = rnorm(n = 1000, mean = 178, sd = 20),
  sigma = runif(n = 1000, min = 0, max = 50)
) %>% 
  # Here, we simulate the data distribution, based on what we decided our prior values to be
  mutate(height = rnorm(n = 1000, mean = mu, sd = sigma))

# Prior Predictive simulation:
# number of lines specified here:
N <- 100
prior <- tibble(
  n = 1:N,
  beta0 = rnorm(n = N, mean = 178, sd = 20),
  beta1 = rlnorm(n = N, meanlog = 0, sdlog = 1)
) %>%
  expand(nesting(n, beta0, beta1), weight = range(data$weight)) %>%
  # Here, we simulate the predictive distribution, based on our model above
  mutate(
    height = beta0 + beta1 * (weight - mean(data$weight))
  )
# We take a look at our prior predictive distribution
dens(prior$height)

# We take a look at the prior predictive distribution lines
prior %>% 
  ggplot(aes(x = weight, y = height, group = n)) +
  geom_line(alpha = 0.10)

avg_weight <- mean(data$weight)
model <- quap(
  alist(
    height ~ dnorm(mu, sigma),                   
    mu <- beta0 + beta1 * (weight - avg_weight), 
    beta0 ~ dnorm(178, 20),                      
    beta1 ~ dlnorm(0, 1),                        
    sigma ~ dunif(0, 50)                         
  ),
  data = data
)
```

We now have a model we can use to predict weights.  
So, using the entire distribution to predict weights..

```{r}
new_indiv <- tibble(
  person = c("person1", "person2", "person3", "person4"),
  weight = c(45, 40, 65, 31)
)

# we simulate the possible predicted heights from each person
heights_predicted <- sim(model, data = list(weight = new_indiv$weight)) %>% 
  as_tibble() %>% 
  rename(
    "person1" = V1,
    "person2" = V2,
    "person3" = V3,
    "person4" = V4
  )
  
height_pred <- heights_predicted %>% 
  summarise(
    "One" = mean(person1),
    "Two" = mean(person2),
    "Three" = mean(person3),
    "Four" = mean(person4),
  ) %>% 
  pivot_longer(
    cols = One:Four,
    names_to = "individual",
    values_to = "expected_height"
  ) %>% 
  transmute(
    individual = individual,
    weight = c(45, 40, 65, 31),
    expected_height = expected_height,
    "interval_low" = c(
      PI(heights_predicted$person1)[1], 
      PI(heights_predicted$person2)[1], 
      PI(heights_predicted$person3)[1], 
      PI(heights_predicted$person4)[1]
    ),
    "interval_high" = c(
      PI(heights_predicted$person1)[2], 
      PI(heights_predicted$person2)[2], 
      PI(heights_predicted$person3)[2], 
      PI(heights_predicted$person4)[2]
    ),
  )

height_pred
```

## Question 2

> Model the relationship between height (cm) and the natural logarithm
> of weight (log-kg): log(weight). Use the entire Howell1 data frame, all
> 544 rows, adults and non-adults. Use any model type from Chapter 4 that
> you think useful: an ordinary linear regression, a polynomial or a spline. I
> recommend a plain linear regression, though. Plot the posterior predictions
> against the raw data.

We take a look at building the model using a similar approach as to above.

```{r}
# Prior Predictive simulation:
# Reload data to include under age 18 persons
data(Howell1)
data.log <- as_tibble(Howell1) %>% 
  mutate(
    weight = log(weight)
  )

avg_weight <- mean(data.log$weight)

## FIXME model isn't scaling logarthmically
## Not sure how to do this one

model2 <- quap( # Fits the model
  data = data.log,
  alist( # Model Definition
    height ~ dnorm(mu, sigma),                   
    mu <-  beta0 + log_b * (weight - avg_weight),
    # Prior defined below:
    beta0 ~ dnorm(178, 20),                      
    log_b ~ dlnorm(meanlog = 0, sdlog = 1),                        
    sigma ~ dunif(0, 50)                         
  )
)

# Predict heights according to model on the log scale
new_weights <- seq(range(data.log$weight))
pred_heights <- sim(model2, data = list(weight = new_weights)) %>% 
                    as_tibble() %>% 
                    rename(
                      "weight" = V1,
                      "height" = V2
                    )

# Plotting
hist(pred_heights$height)
hist(data.log$height)
```
## Question 3

  >Plot the prior predictive distribution for the polynomial regression model
  >in Chapter 4. 
  >You can modify the the code that plots the linear regression
  >prior predictive distribution. 
  >20 or 30 parabolas from the prior should suffice to show where the prior 
  >probability resides. 
  >Can you modify the prior distributions of α, β1, and β2 so that the prior 
  >predictions stay within the biologically reasonable outcome space? 
  >That is to say: Do not try to fit the data by hand. 
  >But do try to keep the curves consistent with what you know about height and 
  >weight, before seeing these exact data.

