---
title: "03Chapter - Statistical Rethinking Notes"
output: 
  github_document:
    pandoc_args: --webtex
---

## Question 1

> The weights listed below were recorded in the !Kung census, but heights
> were not recorded for these individuals. Provide predicted heights and 89%
> compatibility intervals for each of these individuals. That is, fill in the table
> below, using model-based predictions.

So, we look at the data from the !Kung census, by loading the proper data:

```{r setup}
library(rethinking)
library(tidyverse)
data(Howell1)
data <- as_tibble(Howell1)
```

Then we create the prior, filtering heights for ages 18 and over only.

```{r}
# filter out younger than 18

data <- data %>% 
  filter(age >= 18)
```
We consider the simple linear regression model used to predict the effect of height on weight:

height = mu + beta1 *(weight - avg_weight)
```{r}
# Simulate data
prior <- tibble(
  mu = rnorm(n = 1000, mean = 178, sd = 20),
  sigma = runif(n = 1000, min = 0, max = 50)
) %>% 
  # Here, we simulate the data distribution, based on what we decided our prior values to be
  mutate(height = rnorm(n = 1000, mean = mu, sd = sigma))

# Prior Predictive simulation:
# number of lines specified here:
N <- 100
prior <- tibble(
  n = 1:N,
  beta0 = rnorm(n = N, mean = 178, sd = 20),
  beta1 = rlnorm(n = N, meanlog = 0, sdlog = 1)
) %>%
  expand(nesting(n, beta0, beta1), weight = range(data$weight)) %>%
  # Here, we simulate the predictive distribution, based on our model above
  mutate(
    height = beta0 + beta1 * (weight - mean(data$weight))
  )
# We take a look at our prior predictive distribution
dens(prior$height)

# We take a look at the prior predicitve distribution lines
prior %>% 
  ggplot(aes(x = weight, y = height, group = n)) +
  geom_line(alpha = 0.10)

avg_weight <- mean(data$weight)
model <- quap(
  alist(
    height ~ dnorm(mu, sigma),                   
    mu <- beta0 + beta1 * (weight - avg_weight), 
    beta0 ~ dnorm(178, 20),                      
    beta1 ~ dlnorm(0, 1),                        
    sigma ~ dunif(0, 50)                         
  ),
  data = data
)
```

We now have a model we can use to predict weights.  
So, using the entire distribution to predict weights..

```{r}
new_indiv <- tibble(
  person = c("person1", "person2", "person3", "person4"),
  weight = c(45, 40, 65, 31)
)
# we simulate the possible predicted heights from each person
heights_predicted <- sim(model, data = list(weight = new_indiv$weight)) %>% 
  as_tibble() %>% 
  rename(
    "person1" = V1,
    "person2" = V2,
    "person3" = V3,
    "person4" = V4
  ) %>% 
  summarise(
    "p1mean" = mean(person1),
    "p2mean" = mean(person2),
    "p3mean" = mean(person3),
    "p4mean" = mean(person4),
    "p1prob" = PI(person1),
    "p2prob" = PI(person2),
    "p3prob" = PI(person3),
    "p4prob" = PI(person4)
  )

heights_predicted
```

## Question 2

> Model the relationship between height (cm) and the natural logarithm
> of weight (log-kg): log(weight). Use the entire Howell1 data frame, all
> 544 rows, adults and non-adults. Use any model type from Chapter 4 that
> you think useful: an ordinary linear regression, a polynomial or a spline. I
> recommend a plain linear regression, though. Plot the posterior predictions
> against the raw data.

We take a look at building the model using a similar approach as to above.

```{r}
# Prior Predictive simulation:
# number of lines specified here:
N <- 100
prior <- tibble(
  n = 1:N,
  beta0 = rnorm(n = N, mean = 178, sd = 20),
  beta1 = rlnorm(n = N, meanlog = 0, sdlog = 1)
) %>%
  expand(nesting(n, beta0, beta1), weight = range(data$weight)) %>%
  # Here, we simulate the predictive distribution, based on our model above
  mutate(
    height = beta0 + beta1 * (weight - mean(data$weight))
  )
# We take a look at our prior predictive distribution
dens(prior$height)

# We take a look at the prior predicitve distribution lines
prior %>% 
  ggplot(aes(x = weight, y = height, group = n)) +
  geom_line(alpha = 0.10)

avg_weight <- mean(data$weight)
model <- quap(
  alist(
    height ~ dnorm(mu, sigma),                   
    mu <- beta0 + beta1 * (weight - avg_weight), 
    beta0 ~ dnorm(178, 20),                      
    beta1 ~ dlnorm(0, 1),                        
    sigma ~ dunif(0, 50)                         
  ),
  data = data
)
```

