---
title: "Assignment 1"
output: github_document
---
## Question 1
Suppose the globe tossing data (Chapter 2) had turned out to be 4 water in 15 tosses. Contruct the prior distribution, using grid apporximation. Use the same flat prior as in the book.
```{r}
# This is a copy from my notes
p_grid <- seq(from = 0, to = 1, length.out = 20)

# define prior
# our prior is flat
prior <- rep(1, times = 20)

# compute likelihood at each value in grid
# This is where we make the changes in our model.
likelihood <- dbinom(4, size = 15, prob = p_grid)

# compute product of likelihood and prior
unstd.posterior <- likelihood * prior

# standardize the posterior, so it sums to 1
posterior <- unstd.posterior/sum(unstd.posterior)

# Looking at the plot:
plot(p_grid, posterior, type = "b",
     xlab = "probability of water", ylab = "posterior probability")
mtext("Flat Prior")
```

## Question 2
Start over in *1*, but now use a prior that is zero below $$p = 0.5$$ and a constant above $$p = 0.5$$. This corresponds to prior information that a majority of the Earth's surface is water. What difference does the better prior make?

```{r}
# This is a copy from my notes
p_grid <- seq(from = 0, to = 1, length.out = 20)

# define prior
# our prior is not flat, but defined as in question 2.
prior <- ifelse(p_grid < 0.5, 0, 5)

# compute likelihood at each value in grid
# This is where we make the changes in our model.
likelihood <- dbinom(4, size = 15, prob = p_grid)

# compute product of likelihood and prior
unstd.posterior <- likelihood * prior

# standardize the posterior, so it sums to 1
posterior <- unstd.posterior/sum(unstd.posterior)

# Looking at the plot:
plot(p_grid, posterior, type = "b",
     xlab = "probability of water", ylab = "posterior probability")
mtext("Disjoint Prior")
```

A better prior appears to make a better answer to our question, it gives us a better graph. Similarly,  I think if we use appropriate priors, we help set up our inference from the model for success.
