---
title: "Statistical Rethinking: Chapter 8"
output: 
  github_document:
    pandoc_args: --webtex
---

## EDA

Using regularizing priors ("regular priors"), we used in the earlier chapters 
for the frogs data set
### Single level model

$$
\begin{align*}

S_i &\sim \text {Binomial}({\it N_i}, {\it p_i})
\\
\text {logit}({\it p_i}) &= \alpha_{{\small \text{TANK}[i]}} 
\\
{\it \alpha_j} &\sim \text {Normal}(0, 1.5) \quad \text { for } {\it j} = (1, 48)

\end{align*}
$$
And again in code:
```{r Single Level Model, echo=TRUE}
library(rethinking)
data(reedfrogs)
frogs <- reedfrogs
# make the tank cluster variable
frogs$tank <- 1:nrow(frogs)

dat <- list(
  S = frogs$surv,
  N = frogs$density,
  tank = frogs$tank
)

# approximate posterior
m13.1 <- ulam(
  alist(
    S ~ dbinom(N, p),
    logit(p) <- a[tank],
    a[tank] ~ dnorm(0, 1.5)
  ), data = dat, chains = 3, log_lik = TRUE, cmdstan = TRUE
)

# inspect posterior
precis(m13.1, depth = 2)
```
 
### Multilevel Model

$$
\begin{align*}

S_i &\sim \text {Binomial}({\it N_i}, {\it p_i})
\\
\text {logit}({\it p_i}) &= \alpha_{{\small \text{TANK}[i]}} 
\\
{\it \alpha_j} &\sim \text {Normal}(\color{blue}{\bar{\alpha}}, \color{blue}{\sigma}) 
\\
\color{blue}{\bar{\alpha}} &\color{blue}{\sim} \color{blue}{\text{Normal}(0, 1.5)}
\\
\color{blue}{\sigma} &\color{blue}{\sim} \color{blue}{\text{Exponential}(1)}
\end{align*}
$$
We used an adaptive prior for $\alpha_\it{j}$, and set average tank prior as $\bar{\alpha}$, $\sigma$ being the standard deviations of tanks.

Essentially, there are now *two* levels to our model.

Here is the code:
```{r Multilevel Model}
m13.2 <- ulam(
  alist(
    S ~ dbinom(N, p),
    logit(p) <- a[tank],
    a[tank] ~ dnorm(a_bar, sigma),
    a_bar ~ dnorm(0, 1.5),
    sigma ~ dexp(1)
  ), data = dat, chains = 3, log_lik = TRUE, cmdstan = TRUE
)

# We compare the two models
compare(m13.1, m13.2)

# checking sigma
precis(m13.2)
```
The second model was much quicker. Note that sigma is the regularizing prior that was learned from the data.

```{r}
# Extract Stan samples
post <- extract.samples(m13.2)

# compute mean intercept for each tank
# also transform to probability with logistic
frogs$propsurv.est <- logistic(apply(post$a, 2, mean))

# display raw proportions surviving in each tank
plot(frogs$propsurv, ylim = c(0, 1), pch = 16, xaxt = "n",
     xlab = "tank", ylab = "proportion survival", col = rangi2)
axis(1, at = c(1,16,32,48), labels = c(1,16,32,48))

# Overlay posterior means
points(frogs$propsurv.est)

# mark posterior mean probability across tanks
abline(h = mean(inv_logit(post$a_bar)), lty = 2)

# draw vertical dividers between tank densities
abline(v = 16.5, lwd = 0.5)
abline(v = 32.5, lwd = 0.5)
text(8, 0, "small tanks")
text(16+8, 0, "medium tanks")
text(32+8, 0, "large tanks")
```

