---
title: "Data Cleaning - New"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.path = "../Figures/",
  fig.align = "center",
  cache.path = "../Data/cache/"
)
```

## New Project

I am working on a project created from a kaggle data set found here: https://www.kaggle.com/teertha/personal-loan-modeling

I switched to this new project for a number of reasons, including:

* Format is easier to work with
  * No need to download additional packages, download from their website, etc.
* Simpler to model.
  * No topcoded values
  * Raw data
* Topic is more interesting.
* Applies to marketing better
* Response is a logit model

## Data Story

The data set is from Thera Bank customers, including 
demographic information, 
their relationship with the bank, and 
their response to the last personal loan campaign. 
The dataset was generated in a response to a successful campaign by the bank
to increase sign ups for their personal loan product, with a conversion rate of 9%.

Our question is this: what factors make a consumer more likely to sign up for a personal loan?
How much do each of these factors affect the final outcome?

With our response variable set as whether a customer signed up for a personal loan,
the following variables are available in data set:

Variable          | Description
------------------|------------------------------------------------------------
ID                | Unique identifier for each person; Aribtrary numbers
Age               | Customer's age in completed years
Experience        | Number of years of professional experience
Income            | Annual income ($000)
ZIP Code          | Home Address zip code
Family            | Family size of customer
CCAvg             | Avg. spending on credit cards per month ($000)
Education         | Education Level. 1: Undergrad; 2: Graduate; 3: Advanced/Professional
Mortgage          | Value of house mortgage if any. ($000)
Personal Loan     | Did this customer accept the personal loan offered in the last campaign? (response variable)
Securities Account| Does the customer have a securities account with the bank?
CD Account        | Does the customer have a certificate of deposit (CD) account with the bank?
Online            | Does the customer use internet banking facilities?
CreditCard        | Does the customer use a credit card issued by this Bank?

There are no empty values in the data set.  Lets take a look at the data.

## Data Exploration

```{r Reading Data, echo=FALSE}
data <-
  read_csv(
    '../Data/Bank_Personal_Loan_Modelling.csv',
    trim_ws = TRUE,
    col_types = "cddddddddlllll"
  )     
data

data$Family <- factor(data$Family, levels = 1:4, labels = c("One", "Two", "Three", "Four"))
data$Education <- factor(data$Education, levels = 1:3, labels = c("Undergraduate", "Graduate", "Advanced/Professional"))
summary(data)
```

The data set looks good.  Lets take a closer look at our distributions. 
I'm curious about the customer demographics.

```{r Customer Demographics}
ggplot(data = data) +
  geom_histogram(aes(x = Age, color = Education), binwidth = 1) + 
  labs(title = "Customer Demographics", y = "Count") +
  theme_bw()
summary(data$Age)
```

It appears we have a good spread of ages and education levels, 
with a minimum age of 23, 
and a max of 67. 
It also appears we have a roughly proportional number of different Education levels 
across our data set.  
This will make for some good predictions.

Lets look at the spread of income next.

```{r Income}
ggplot(data, mapping = aes(x = Income)) +
  geom_density() +
  labs(x = "Income per Year (in Thousands $)", y = NULL, title = "Customer Income")
summary(data$Income)
```
It appears our incomes are heavily right skewed, which is hardly surprising. 
Taking a look at mortgage next:

```{r Mortgage}
ggplot(data) +
  geom_density(aes(x = Mortgage)) +
  xlim(c(1, 600)) # Removed large number of zeros from displaying
```
Please note, I removed a large number of values that were zero. 
Also extremely right skewed, with a majority having paid off their mortgage. 
It may be this data set is only counting mortgages with the bank, 
so maybe it's not the most reliable predictor.

```{r Family Stats}
ggplot(data, mapping = aes(y = Income)) +
  geom_boxplot(aes(x = Family))

ggplot(data, mapping = aes(x = Income)) +
  geom_histogram(fill = "white", color = "black", bins = 100) +
  facet_grid(Family ~ .) +
  labs(title = "Income Distribution vs. Family Size", y = NULL) +
  theme_bw()
```

It appears income is strangely distributed. Accounts holders with family sizes of
1 and 2 have a much wider range in income levels. 
This may be due to couples with double income, so we will have to account for this effect later.

```{r Zip Codes}
# Display mean and sd of Quantitative data, by Zip Code
zip_data <- data %>%
  group_by(`ZIP Code`) %>%
  summarize(across(where(is.double), list(mean = mean, sd = sd)))

zip_data
tab_summary <- summary(zip_data)
tbl <- tab_summary %>% 
  knitr::kable(padding = 1 ) %>%
  str_replace_all(pattern = "(?<replace>((?<=\\|)((\\w+).?( +)?(\\w+.?)?( +)?:( +)?)))", replacement = " ") %>% 
  str_split(pattern = "( +)?\\|( +)?")

tbl <- tbl %>%  as_tibble(.name_repair = 'minimal')
tbl[,1] <- NULL
tbl[,1] <- NULL
names(tbl) <- c("Min", "1st Q", "Median", "Mean", "3rd Q", "Max", "NA's")
tbl %>% knitr::kable(padding = 1, caption = "Data variation by Zip Code")
# 
# 
# plot1 <- ggplot(zip_data, mapping = aes(x = Age_mean, y = Age_sd)) +
#   geom_point() +
#   geom_density_2d() +
#   theme(aspect.ratio = 1) +
#   labs(title = "Age", x = "Mean", y = "StdDev")
# 
# plot2 <- ggplot(zip_data, mapping = aes(x = Experience_mean, y = Experience_sd)) +
#   geom_point() +
#   geom_density_2d() +
#   theme(aspect.ratio = 1) +
#   labs(title = "Experience", x = "Mean", y = "StdDev")
# 
# plot3 <- ggplot(zip_data, mapping = aes(x = Income_mean, y = Income_sd)) +
#   geom_point() +
#   geom_density_2d() +
#   theme(aspect.ratio = 1) +
#   labs(title = "Income", x = "Mean", y = "StdDev")
# 
# plot4 <- ggplot(zip_data, mapping = aes(x = CCAvg_mean, y = CCAvg_sd)) +
#   geom_point() +
#   geom_density_2d() +
#   theme(aspect.ratio = 1) +
#   labs(title = "CCAvg", x = "Mean", y = "StdDev")
# 
# plot5 <- ggplot(zip_data, mapping = aes(x = Mortgage_mean, y = Income_sd)) +
#   geom_point() +
#   geom_density_2d() +
#   theme(aspect.ratio = 1) +
#   labs(title = "Experience", x = "Mean", y = "StdDev")
# 
# print(list(plot1, plot2, plot3, plot4, plot5))
```
There is a definite effect here of the zip code, just given the variation.


Lets look at the relationships between the variables:

```{r Correlation Plot}
data <-
  read_csv(
    './Project/Data/Bank_Personal_Loan_Modelling.csv',
    trim_ws = TRUE,
    col_types = "cddddddddlllll"
  ) 

corrplot::corrplot(cor(data %>% select(-ID)), type = "upper")
```
According to the plot, 
there may be some collinearity between the `Income` and `CCAvg` variables,
which makes sense, 
because *if you make more money*, you are also likely to *spend* more.

Age and Experience are also highly correlated, which also makes sense, 
because people with more experience almost always tend to be older.

None of the other variables seem to have any concerning multicollinearity.

I also note that the presence of a CD account with the Bank also seems to 
correlate with accepting the personal loan campaign, 
so we may be seeing the effects of some brand loyalty here.

Of all the variables, income seems to be among the best predictors 
for the personal loan acceptance. We'll keep that in mind as we build our model.
