---
title: "03 - Analysis"
output: github_document
---

## Fixing the Model

So it turns out I was running the model wrong, as I thought I was using standardized values, when in fact I was not.



```{r setup, include=FALSE}
library(dagitty)
library(rethinking)
library(cmdstanr)
library(tidyverse)
knitr::opts_chunk$set(
  fig.path = "../Figures/",
  fig.align = "center",
  cache.path = "../Data/cache/"
)

data <-
  read_csv(
    '../Data/Bank_Personal_Loan_Modelling.csv',
    trim_ws = TRUE,
    col_types = "cddddddddlllll"
  )     
data_numeric <- data %>% select(-ID)

data$Family <- factor(data$Family, levels = 1:4, labels = c("One", "Two", "Three", "Four"))
data$Education <- factor(data$Education, levels = 1:3, labels = c("Undergraduate", "Graduate", "Advanced/Professional"))



```
I want to check out the relationship between some of the variables before I continue again.

```{r Correlation Plot}
data_numeric %>% cor() %>% corrplot::corrplot(type = "upper")
```

```{r Checking Relationships}
ggplot(data, mapping = aes(x = Experience, y = Income)) +
  geom_jitter(aes(color = Education, alpha = 0.5))
```
It generally appears that many undergraduates make more than the other education levels
at all years of experience. This may be due to the Double Income effect I talked about earlier.

```{r Family 1}
ggplot(data, mapping = aes(x = Experience, y = Income)) +
  geom_jitter(aes(color = Education, alpha = 0.5)) +
  facet_wrap(~Family)
```

As suspected, there appears to be a relationship. Many people with a family size of 3 or higher appear to make much less than undergraduates who have a family size of 1 or 2.
Probably due to the double income effect.

Assuming Incomes are highly right skewed definitely seems to be the case for family sizes of 3 and four. I wonder if we use Age rather than experience what patterns will appear.

```{r Family 2}
ggplot(data, mapping = aes(x = Age, y = Income)) +
  geom_jitter(aes(color = Education, alpha = 0.5)) +
  facet_wrap(~Family)
```

As expected, the graphs look strikingly similar. I want to look at these factors in terms of the response.

```{r Family 3}
ggplot(data, mapping = aes(x = Experience, y = `Personal Loan`)) +
  geom_jitter(aes(color = Education, alpha = Income)) +
  facet_wrap(~Family)
```

I find it interesting that people with family sizes of one and two, hardly any undergraduate educated folks accepted the personal loan campaign. Most of them are Graduated. Age or experience level doesn't necessicarily have a huge impact here.

I wonder about credit card balance..

```{r Family 4}
ggplot(data, mapping = aes(x = CCAvg, y = `Personal Loan`)) +
  geom_jitter(aes(color = Education, alpha = Income)) +
  facet_wrap(~Family)
```

Strange gap in the graph on two, centered around 5 grand. Huh.

In general, my what we've seen so far seems to imply that for folks with a family size of one or two, education level seems to be driving factor, where more educated folks tend to accept a personal loan than undergraduates.  

When we look at families of size 3 or 4, it doesn't seem to matter as much. But for those groups, it seems a low CC balance is an indicator that they probably will not accept a personal loan.

```{r Family 5}
ggplot(data, mapping = aes(x = CCAvg, y = `Personal Loan`)) +
  geom_jitter(aes(color = Income)) +
  facet_wrap(~Family)
```

Individuals with higher incomes and smaller families tend to have higher credit card balances, but not always. 

Individuals with large families, and low incomes tend to have low credit card balances, and are less likely to accept a personal loan.

```{r CD Account}
data %>% 
  select(`Personal Loan`, `Securities Account`, `CD Account`, Online, CreditCard) %>% 
  cor() %>% 
  corrplot::corrplot(method = "circle", type = "upper")


ggplot(data, mapping = aes(y = `Personal Loan`)) +
  geom_jitter(mapping = aes(x = Family )) +
  facet_wrap(~`CD Account`)
```
Looking at the first graph, we see that generally, if someone had a CD Account with the bank, they also would be more likely get a personal loan from them. There are also more individuals who seemed equally as likely to get a personal loan if they already had a CD account.


```{r Mortgage and Family}
ggplot(data, mapping = aes(x = Age, y = Mortgage)) +
  geom_density_2d() +
  geom_jitter(aes(color = Family))
```

There appears to be a group of individuals who have mortgages closer around 100 grand, ranging in age from about 30, to 60 years old.

```{r Mortgage vs Response}
ggplot(data, mapping = aes(y = `Personal Loan`)) +
  geom_jitter(mapping = aes(x = Mortgage, alpha = Income )) +
  facet_wrap(~`CD Account`)
```
People with higher mortgages also tended towards getting a personal loan.
Also people with higher incomes generally had higher mortgages.


```{r Family: Mortgage vs Response}
ggplot(data) +
  geom_jitter(aes(y = `Personal Loan`, x = Mortgage)) +
  facet_wrap(~Family)
```

```{r Correlation by Family size}
byFamCor <- data_numeric %>% split(.$Family) %>%
  map(select, -Family) %>% 
  map(cor) %>% 
  map(corrplot::corrplot, type = "upper")
```

Income and CCAvg seems to generally have a larger effect on personal loan for family sizes of 3 or more.

```{r Family vs CC}
ggplot(data) +
  geom_jitter(aes(x = Family, y = CCAvg, color = Income))
```
Also of note, that Families of 3 or 4 either have very low credit card balances (mostly at lower income levels), or relatively high CC balances. 

I selected the following variables:
    - Family
    - Income
    - CCAvg

```{r New Model, eval = FALSE}
loan ~ Binomial(1, p)
logit(p) <- alpha[Family] + alpha[Family]*(CCAvg + Income) + CCAvg + Income
Family ~
CCAvg
Income
```

```{r New Model: Data list}
data_list <- list(
  loan = as.numeric(data$`Personal Loan`),
  income = standardize(data$Income),
  ccavg = standardize(data$CCAvg),
  family = as.numeric(data$Family)
)
```

And now we fit a baseline model, using varying intercepts based on Family size:

```{r fit3, cache=TRUE, dependson="New Model: Data list"}
fit3 <- ulam(
  alist(
    loan ~ dbinom(1, p),
    logit(p) <- alpha[family] + beta_ccavg * ccavg + beta_income * income,
    alpha[family] ~ dnorm(alpha_bar, sigma),
    beta_ccavg ~ dnorm(0, 1.5),
    beta_income ~ dnorm(0, 1.5),
    alpha_bar ~ dnorm(0, 1.5),
    sigma ~ dexp(1)
  ),
  data = data_list,
  log_lik = TRUE,
  chains = 2,
  cores = 4,
  cmdstan = TRUE
)
save(fit3, file = "../Data/cache/fit3")

precis(fit3)
```

I bet the effect family size is having on income and ccavg is confounding. Maybe I will try adding an interaction effect.

```{r fit4, cache=TRUE, dependson="New Model: Data list"}
fit4 <- ulam(
  alist(
    loan ~ dbinom(1, p),
    logit(p) <- alpha[family] + beta_ccavg * ccavg + beta_income * income + alpha[family] * (ccavg + income),
    alpha[family] ~ dnorm(alpha_bar, sigma),
    beta_ccavg ~ dnorm(0, 1.5),
    beta_income ~ dnorm(0, 1.5),
    alpha_bar ~ dnorm(0, 1.5),
    sigma ~ dexp(1)
  ),
  data = data_list,
  log_lik = TRUE,
  chains = 4,
  cores = 4,
  cmdstan = TRUE
)

precis(fit4)
```

Just based off the n_eff, I think the interaction effect is better left off.

Though the Rhat suggests that the variables are well fitted, I don't think we explored the posterior efficiently enough to deal with all the data. Part of the data (I would imagine because of the double income effect) cannot be adequately explained by the model.

```{r Trace Plot 3, 4}
# traceplot(fit3)
# traceplot(fit4)
```

