---
title: "Data Story"
output: github_document
---

## Initial Model

The variables available to me are:

* ID
* Age
* Experience
* Income
* ZIP Code
* Family
* CCAvg
* Education
* Mortgage
* Personal Loan
* Securities Account
* CD Account
* Online
* CreditCard

ID is just a simple row index, so that will obviously be excluded.

##### Variables

* Age
* Experience
* Income
* ZIP Code
* Family
* CCAvg
* Education
* Mortgage
* Securities Account
* CD Account
* Online
* CreditCard

##### Response

* Personal Loan

```{r Setup, echo=FALSE}
library(dagitty)
library(rethinking)
library(cmdstanr)
library(tidyverse)

```
### Creating The Model

```{r Read in Data, echo=FALSE}
data <-
  read_csv(
    './Project/Data/Bank_Personal_Loan_Modelling.csv',
    trim_ws = TRUE,
    col_types = "cddddddddlllll"
  ) 
```

I will initially set the priors as flat. We will start with a small number of predictors.

```{r Intial Modle Priors, eval=FALSE,echo=FALSE}
loan ~ binomial(1, p) # Binomial distribution of likelihood to accept the personal loan
logit(p) = beta_age  + beta_income + beta_ccavg  # logit model for acceptance of loan likelihood
beta_age ~ normal(0, 0.01 )          # Effect of Age on loan acceptance 
beta_income ~ normal(0, 0.01)        # Effect of income
beta_ccavg ~ normal(0, 0.01)         # Effect of average credit card balance
```

### Running the Model

Just using the initial model, to see what the output looks like. Binomial regression
with a logit link function for the liklihood of a person getting a loan.

```{r Running the Initial Model, cache=TRUE}
# Create data list
loan_list <- list(
  loan = data$`Personal Loan`,
  age = data$Age,
  income = data$Income,
  ccavg = data$CCAvg
)

# Fitting the Initial Model
fit01 <- ulam(
  alist(
    loan ~ dbinom(1, p),
    logit(p) <-  beta_age * age + beta_inc * income + beta_cc * ccavg,
    beta_age ~ dnorm(0, 0.5),
    beta_inc ~ dnorm(0, 1),
    beta_cc ~ dnorm(0, 1.5)
  ),
  data = loan_list,
  log_lik = TRUE,
  chains = 4,
  cores = 4,
  cmdstan = TRUE
)
```

Stan didn't like that very much, probably because the priors are trash, and not very informative.

I will try again to pick initial priors that fit better with the data.
It's not worth checking the model, so we are going to iterate again.

### Rethinking the Model

The previous model had too many divergent transitions, so we are going to be more
thoughtful about this model.

Let's assume there is a default value of a conversion rate of 5%, 
just based on my experience in keyword advertising, that would be a good rate.
So, we add a `beta0 ~ Normal(mu = 0.05, sigma = 0.01)`

I also wanted to revisit the DAG for this model to see 
if I should include any other variables. 

```{r DAG 1}
dag01 <- dagitty("dag {
                 Age -> Loan
                 Income -> Loan
                 Age -> Income
                 }")

coordinates(dag01) <- list(x = c(Age = 0, Loan = 1, Income = 2), y = c(Age = 0, Loan = 1, Income = 0))
plot(dag01)
```

We have to assume that overall income has *some* influence on wage. However,
this model is complicated by the fact that the reported income values are 
overall household income,
some of which are most definitely double income households. 

So, drawing our DAG again, this time including the variables `Family` and `CCAvg`.

```{r DAG 2}
dag02 <- dagitty("dag {
                 Age -> Loan
                 Income -> Loan
                 Age -> Income
                 Age -> Family
                 Income -> Credit
                 Family -> Income
                 Credit -> Loan
                 }")

coordinates(dag02) <- list(x = c(Age = 2, Loan = 2, Income = 1, Credit = 0, Family = 0 ), 
                           y = c(Age = 0, Loan = 2, Income = 1, Credit = 2, Family = 0))
plot(dag02)
```



I also want to measure the difference of the model with and without the `CCAvg` variable 
to see if our model makes some better predictions.


```{r fit2, cache=TRUE}
fit02 <- ulam(
  alist(
    loan ~ dbinom(1, p),
    logit(p) <- beta0 + beta_age * age + beta_inc * income,
    beta0 ~ dnorm(0.05, 0.01),
    beta_age ~ dnorm(0, 0.5),
    beta_inc ~ dnorm(0, 1)
  ),
  data = loan_list,
  log_lik = TRUE,
  chains = 4,
  cores = 4,
  cmdstan = TRUE
)
```

I think Stan liked this model much better. Let's take a look at what we have here:

```{r fit2 evaluation, cache=TRUE}
# precis(fit02)
# show(fit02)
# 
# prior02 <- extract.prior(fit02)
# 
# p <- link(fit02, post = prior02, data = list(age = c(-2, 2)))
```


